**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-13 paper/4_WIP/manuscript.qmd
minute changes to manuscript

The short version of the State-Trait Anxiety Inventory [STAI-5, @zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI [@marteau1992development] includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

@@

The original or refined version of the PHQ-4 was followed by the BDI-II, STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and were only used as part in this study of participation quality control.

>>>>

The short version of the State-Trait Anxiety Inventory [STAI-5, @zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI [@spielberger1970manual] includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

@@

The original or refined version of the PHQ-4 was followed by the BDI-II, STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and ere only used in this stud as part of data quality control checks.
